%%% Parte de la Guia Completa a Linux ver 1.2.2
%%% de Jaime E. Gomez <jgomez@uniandes.edu.co>
%%% http://linuxcol.uniandes.edu.co/infolinux/docs/guia_linux/guia_linux.html
\porcion{Iniciando la instalación}
\autor{\jeg}
\colaborador{\SGG}
\revisor{}
\traductor{}

\tablefirsthead{\hline Paquete & Descripción\\}
\tablehead{\hline \multicolumn{2}{|l|}%
	{\footnotesize\slshape continuación de la página anterior}\\
\hline
Paquete & Descripción\\ \hline}

\tabletail{\hline}

\begin{center}
\scriptsize{
\begin{supertabular}{|p{3.2cm}|p{7.2cm}|}
\hline
acon & Arabic support for linuxconsole \\
acpid & ACPI kernel daemon and control utility \\
adjtimex & A utility for adjusting kernel time variables. \\
adns & Advanced, easy to use, asynchronous-capable DNS client \\
aethera & Aethera - Email and PIM application for \\
alsa-lib & Advanced Linux Sound Architecture (ALSA) lib \\
alsa-utils & Advanced Linux Sound Architecture (ALSA) utils \\
ammonite & Ammonite is a portion of the Eazel \\
ammonite-devel & Libraries and include files for developing Ammonite \\
am-utils & Automount utilities including an updated version of \\
anacron & A cron-like program that doesn't go by \\
apache-common & Files common for apache and apache-mod\_perl install \\
apache-conf & Configuration files for Apache \\
apache-mod\_perl & Apache Web server with a built-in Perl \\
apache-modules & Standard modules for Apache \\
apache-suexec & Suexec binary for apache \\
apache & The most widely used Web server on \\
apmd & Advanced Power Management (APM) BIOS utilities for \\
arpwatch & Network monitoring tools for tracking IP addresses \\
arts & An Analog RealTime Synthesizer \\
ash & A smaller version of the Bourne shell. \\
ash-static & A smaller version of the Bourne shell \\
aspell & An Open Source interactive spelling checker program. \\
aspell-en & American dictionary \\
aterm & An rxvt-based terminal emulator for X11 \\
at & Job spooling tools. \\
audiofile & Library to handle various audio file formats. \\
aumix & A GTK+/Ncurses audio mixer \\
Aurora & Graphical bootup for Linux \\
Aurora-Monitor-NewStyle-Categorizing-WsLib & New-style, Categorizing, WsLib based \\
Aurora-Mon-NewStyle-WsLib & New-style, WsLib based \\
Aurora-Monr-Trad-Gtk+ & Traditional look, X/Gtk+ based \\
Aurora-Monr-Trad-WsLib & Traditional look, WsLib based \\
auth\_ldap & This is a LDAP authentication module for \\
autoconf & A GNU tool for automatically configuring source \\
autofs & A tool for automatically mounting and unmounting \\
autologin & Automatically log in \\
automake & A GNU tool for automatically creating Makefiles. \\
awesfx & Utility programs for the AWE32 sound driver \\
balsa & Balsa Mail Client \\
basesystem & The skeleton package which defines a simple \\
bash & The GNU Bourne Again shell (bash). \\
Bastille & Bastille tightens security on a Mandrake or \\
Bastille-Chooser & BastilleChooser helps a new user choose a \\
Bastille-Curses-module & This module provides Bastille-perl-UI-module. \\
Bastille-Tk-module & This module provides Bastille-perl-UI-module. \\
bc & GNU's bc (a numeric processing language) and \\
bdflush & The process which starts the flushing of \\
bind & A DNS (Domain Name System) server. \\
bind-utils & Utilities for querying DNS name servers. \\
binutils & GNU Binary Utility Development Utilities \\
bison & A GNU general-purpose parser generator. \\
blackbox & A Window Manager for the X Window \\
bonobo & Library for compound documents in GNOME \\
bootparamd & A server process which provides boot information \\
bug-buddy & Utility to ease the reporting of bugs \\
byacc & A public domain Yacc parser generator. \\
bzip2 & Extremely powerful file compression utility \\
caching-nameserver & The configuration files for setting up a \\
cdialog & A utility for creating TTY dialog boxes. \\
cdp & An interactive text-mode program for controlling audio \\
cdparanoia & Utility to copy digital audio cd's. \\
cdrecord & A command line CD/DVD-Recorder \\
cdrecord-cdda2wav & CD-Audio to .wav converter \\
chkconfig & A system tool for maintaining the /etc/rc0.d, \ldots \\
chkfontpath & Simple interface for editing the font path \\
chromium & Fast paced, arcade-style, top-scrolling space shooter \\
chromium-setup & Setup frontend for Chromium \\
cim & Simula to C translator. Mother of all \\
clanlib & The ClanLib Game SDK \\
cleanfeed & A spam filter for Usenet news servers. \\
common-licenses & Contains the various common licenses uses by \\
console-tools & Linux console tools \\
control-center & The GNOME control center. \\
cpio & A GNU archiving program. \\
cproto & Generates function prototypes and variable declarations \\
cracklib & A password-checking library. \\
cracklib-dicts & The standard CrackLib dictionaries. \\
crontabs & Root crontab files used to schedule the \\
ctags & Generates an index (or "tag") file for \\
cttex & Cttex, Thai word separator program \\
cups-common & Common Unix Printing System - Common stuff \\
cups & Common Unix Printing System - Server package \\
cups-drivers & Common Unix Printing System - Drivers (all) \\
cvs & A version control system \\
cyrus-sasl & SASL is the Simple Authentication and Security \\
db1 & The BSD database library for C (version \\
db1-tools & Tools for Berkeley DB (version 1) library. \\
db2 & The BSD database library for C (version \\
db3-devel & Development libraries/header files for the Berkeley DB \\
db3 & The Berkeley DB database library for C. \\
detect & Hardware detection library \\
detect-lst & Hardware list for the detection library \\
dev86 & A real mode 80x86 assembler and linker. \\
devfsd & Daemon for providing old entries in /dev \\
dev & The most commonly-used entries in the /dev \\
dhcp & A DHCP (Dynamic Host Configuration Protocol) server \\
dhcpcd & DHCPC Daemon \\
dhcp-client & A DHCP (Dynamic Host Configuration Protocol) client. \\
dhcpxd & DHCPXD Daemon \\
dia & A gtk+ based diagram creation program. \\
diffstat & A utility which provides statistics based on \\
diffutils & A GNU collection of diff utilities \\
dip & Handles the connections needed for dialup IP \\
docbook-dtd412-xml & XML document type definition for DocBook 4.1.2. \\
docbook-dtd41-sgml & SGML document type definition for DocBook 4.1. \\
docbook-style-dsssl & Norman Walsh\'s modular stylesheets for DocBook. \\
dosfstools & Utilities to create and check MS-DOS FAT \\
DrakConf & The Mandrake Control Center \\
DrakeLogo & Small utility to easily change the boot-up \\
drakfloppy & Graphical front end of mkbootdisk. \\
drakfont & TrueType fonts manager \\
drakprofile & Hardware profile switching tool for laptops \\
draksync & Graphical tool for directory synchronization \\
drakxtools-newt & The drakxtools (XFdrake, diskdrake, \ldots ) \\
drakxtools & The drakxtools (XFdrake, diskdrake, \ldots) \\
dump & Programs for backing up and restoring filesystems \\
e2fsprogs & Utilities used for the second extended (ext2) \\
ed & The GNU line editor. \\
ee & The Electric Eyes image viewer application. \\
efax & A program for faxing using a Class \\
egcs-cpp & The GNU C-Compatible Compiler Preprocessor \\
egcs & The GNU Compiler Collection \\
eject & A program that ejects removable media using \\
elm & The elm mail user agent. \\
emacs-leim & Emacs Lisp code for input methods for \\
emacs-nox & The Emacs text editor without support for \\
emacs & The libraries needed to run the GNU \\
emacs-X11 & The Emacs text editor for the X \\
enscript & Converts plain ASCII to PostScript. \\
eperl & An extension to perl that turns it \\
esound & The Enlightened Sound Daemon \\
etcskel & Linux Mandrake default files for new users' \\
everybuddy & Instant messaging client \\
evolution & Integrated GNOME mail client, calendar and address \\
expat-devel & Development environment for the expat XML parser \\
expat & Expat is an XML parser written in \\
ext2ed & An ext2 filesystem editor. \\
ext2resize & ext2fs resizer. \\
faces & A list monitor with a visual output \\
faq & Frequently Asked Questions (FAQ) about Linux \\
fbset & Framebuffer utilities for changing video modes. \\
fetchmail & Full-featured POP/IMAP mail retrieval daemon \\
file & A utility for determining file types. \\
filesystem & The basic directory layout for a Linux \\
fileutils & The GNU versions of common file management \\
findutils & The GNU versions of find utilities (find, \\
finger & The finger client. \\
flex & A tool for creating scanners (text pattern \\
fmirror & FTP mirroring package \\
fortune-mod & A program which will display a fortune. \\
freeswan & A Free IPSEC implemetation \\
freetype2 & FreeType2 \\
freetype & Free TrueType font rasterizer library. \\
freetype-tools & Tools to manipulate TTF fonts \\
fribidi & library to support Bi-directional scripts \\
ftp & The standard UNIX FTP (file transfer protocol) \\
fwhois & A finger-style whois program. \\
gabber & Gabber is a GNOME client for an \\
gaddr & Simple little address book \\
gaim & A client compatible with AOL's 'Instant Messenger' \\
gated & The GateD routing daemon. \\
gawk & The GNU version of the awk text \\
gcc-c++ & C++ support for gcc \\
gcc-colorgcc & Gcc output colorizer \\
gcc-cpp & The C Preprocessor \\
gcc-g77 & Fortran 77 support for gcc \\
gcc-objc & Objective C support for gcc \\
gcc & Various compilers (C, C++, Objective-C, ...) \\
GConf & GConf is a configuration database system. \\
gda-postgres0 & GDA PostgreSQL Provider \\
gdb & A GNU source-level debugger for C, C++ \\
gdk-pixbuf & An image loading and rendering library for \\
gdk-pixbuf-gnomecanvas & An image loading and rendering library for \\
gdk-pixbuf-loaders & An image loading and rendering library for \\
gdk-pixbuf-xlib & An image loading and rendering library for \\
gdm & The GNOME Display Manager. \\
gd-utils & The Utils files for gd. \\
gedit & gEdit is a small but powerful text \\
gettext-base & GNU libraries and utilities for producing multi-lingual \\
gettext & GNU libraries and utilities for producing multi-lingual \\
getty\_ps & The getty and uugetty programs. \\
gftp & Multithreaded FTP client for X Windows \\
ghostscript-fonts & Fonts for the GhostScript PostScript(TM) interpreter. \\
ghostscript-module-X & PostScript interpreter and renderer (additional support for \\
ghostscript & PostScript interpreter and renderer, all printer drivers \\
ghostscript-utils & Additional tools for configuring printers \\
giftrans & A program for making transparent GIFs from \\
gimp & The GNU Image Manipulation Program \\
glibc-devel & Header and object files for development using \\
glibc-profile & The GNU libc libraries, including support for \\
glibc & The GNU libc librairies \\
Glide\_V2 & Glide runtime for 3Dfx Voodoo2 boards \\
Glide\_V3-DRI & Glide runtime for 3Dfx Voodoo Banshee and \\
Glide\_V3 & Glide runtime for 3Dfx Voodoo Banshee and \\
Glide\_V5 & Glide runtime for 3Dfx Voodoo Banshee and \\
glimmer & Extensible Code Editor \\
gltron & Gltron, a 3d lightcycle game using OpenGL \\
gmc & Midnight Commander visual shell (GNOME version) \\
gnobog & Gnome Bookmarks Organizer \\
gnomba & Gnome SMB Browser \\
gnome-applets & Small applications which embed themselves in the \\
gnome-audio & Sounds for GNOME events. \\
gnome-chess & GNOME chess \\
gnome-core & The core programs for the GNOME GUI \\
gnome-iconedit & Icon editor for GNOME \\
gnomeicu & Gnome ICQ communications program \\
gnome-libs-devel & Libraries and headers for GNOME application development \\
gnome-libs & Main GNOME libraries \\
gnome-linuxconf & The GNOME front-end for linuxconf. \\
gnome-media & GNOME media programs \\
gnomemm & A C++ interface for Gnome libs (a \\
gnome-network & GNOME network programs \\
gnome-objc & GNOME Objective C libraries \\
gnome-pilot & GNOME Pilot programs \\
gnome-pim & The GNOME Personal Information Manager. \\
gnome-print & Printing libraries for GNOME. \\
gnome-tiles & Desktop Background Images for GNOME \\
gnome-toaster & CD-Recording frontend for GNOME \\
gnome-utils & GNOME utility programs such as file search \\
gnome-vfs & GNOME virtual file-system libraries \\
gnorpm & A graphical front-end to RPM for GNOME. \\
gnozip & Graphical interface for compression utilities \\
gnumeric & A full-featured spreadsheet for GNOME. \\
gnupg & GNU privacy guard - a free PGP \\
gnus-emacs & Gnus Newsreader for Emacs \\
gphoto & gPhoto - the GNU Digital Camera Program \\
gpm & A mouse server for the Linux console \\
g-print & Drag'n'Drop printing on GNOME \\
gqview & Graphics file browser utility \\
grep & The GNU versions of grep pattern matching \\
grip & Grip, a CD player and ripper/MP3-encoder front-end \\
groff & A document formatting system \\
groff-for-man & Parts of the groff formatting system that \\
grpmi & GUI frontend for rpms installation or upgrade \\
grub & GRand Unified Bootloader \\
gtkdialogs & Ready-to-use gtk+ dialog boxes \\
gtk-engines & Default GTK+ theme engines. \\
gtkhtml & GtkHTML is a HTML rendering/editing library. \\
gtk+mdk & Mandrake specific GTK+ Widgets \\
gtml & An html preprocessor \\
gtop & The GNOME system monitor. \\
guile & A GNU implementation of Scheme for application \\
gurpmi & User mode rpm GUI install \\
gv & An enhanced front-end for the ghostscript PostScript(TM) \\
GXedit & A multi-function text editor using GTK+ \\
gzip & The GNU data compression program \\
harddrake & Main Hardware Configuration/Information Tool \\
hdparm & A utility for displaying and/or setting hard \\
hexedit & View and edit files in hexadecimal or \\
howto-html-en & HOWTO documents (html format) from the Linux \\
howto-utils & Index generator for html formatted HOWTO documents \\
htdig & A web indexing and searching system for \\
icepref & IceWm configurator \\
icewm-light & A light version of Icewm \\
icewm & X11 Window Manager \\
ImageMagick & An X application for displaying and manipulating \\
ImageMagick-lib & Modules for ImageMagick \\
imap & Server daemons for IMAP and POP network \\
imlib & An image loading and rendering library for \\
imlib-cfgeditor & A configuration editor for the Imlib library. \\
imwheel & A utility to make wheel mice work \\
indent & A GNU program for formatting C code. \\
indexhtml & Mandrake html welcome page \\
info & A stand-alone TTY-based reader for GNU texinfo \\
info-install & Program to update the GNU texinfo documentation \\
initscripts & The inittab file and the /etc/init.d scripts. \\
inn & The InterNetNews (INN) system, an Usenet news \\
intimed & A time server for synchronizing networked machines' \\
ipchains & IP Firewalling Chains. \\
iproute2 & Advanced IP routing tools \\
iptables & Tools for managing Linux kernel packet filtering \\
iputils & The ping program for checking to see \\
ipxutils & Tools for configuring and debugging IPX interfaces \\
irssi & Irssi is an IRC client \\
isapnptools & Utilities for configuring ISA Plug-and-Play (PnP) devices \\
isdn4k-utils & Bundled Utilities for configuring an using ISDN4Linux \\
isdn4net & Networking with the isdn subsystem \\
ispell-de & German files for ispell \\
ispell-en & English dictionary for ispell \\
ispell-es & Spanish files for ispell \\
ispell-fr & French files for ispell \\
ispell-it & Italian files for ispell \\
ispell & The GNU interactive spelling checker program \\
jabber & Jabber is an instant messaging System. \\
jbigkit & The JBIG Kit \\
jed-common & Files needed by any Jed editor. \\
jed-xjed & The X Window System version of the \\
joe & An easy to use, modeless text editor. \\
jpilot & palm pilot desktop for Linux \\
jpilot-plugin-devel & library and header file needed for jpilot \\
kdeadmin & K Desktop Environment - Adminstrative Tools \\
kdebase & K Desktop Environment - Core files \\
kdegraphics & K Desktop Environment - Graphics \\
kde-i18n-de & German language support for KDE \\
kde-i18n-es & Spanish language support for KDE \\
kde-i18n-fr & French language support for KDE \\
kde-i18n-it & Italian language support for KDE \\
kde-i18n-uk & Ukrainian language support for KDE \\
kde-i18n-zh\_CN.GB2312 & Chinese (Simplified Chinese) language support for KDE \\
kde-i18n-zh\_TW.Big5 & Chinese (Big5) language support for KDE \\
kdelibs-devel & Header files and documentation for compiling KDE \\
kdelibs & K Desktop Environment - Libraries \\
kdemultimedia & K Desktop Environment - Multimedia \\
kdenetwork & K Desktop Environment - Network Applications \\
kdepim & K Desktop Environment - Person Information Management \\
kdesdk & K Desktop Environment - Software Development Kit \\
kdesupport-devel & Header files and documentation for KDE Support \\
kdesupport & K Desktop Environment - Support Libraries \\
kdetoys & K Desktop Environment - Toys and Amusements \\
kdeutils-devel & K Desktop Environment - Utilities - Headers \\
kdeutils & K Desktop Environment - Utilities \\
kdevelop & Integrated Development Environment for C++/C \\
kdoc & K Desktop Environment - Documentation tools \\
kernel22-smp & The Linux Kernel compiled for SMP machines. \\
kernel22 & The Linux kernel (the core of the \\
kernel-headers & Header files for the Linux kernel. \\
kernel-pcmcia-cs & The daemon and device drivers for using \\
kernel-smp & The Linux Kernel compiled for SMP machines. \\
kernel & The Linux kernel (the core of the \\
kinput2-wnn4 & Kinput2 for Wnn4 \\
kmago & Kmago is a frontend to GNU wget \\
koffice & Set of office applications for KDE \\
kon2 & KON - Kanji ON Linux console \\
ksymoops & Tool for decoding Ooops from the kernel \\
kterm & A Kanji (Japanese character set) terminal emulator \\
kudzu & The Linux hardware probing tool. \\
kups & A KDE-based printer administration tool for CUPS \\
kvirc & Visual IRC client \\
ldconfig & Creates a shared library cache and maintains \\
ldetect-devel & Development package for ldetect \\
ldetect & Light hardware detection library \\
ldetect-lst-devel & Devel for ldetect-lst \\
ldetect-lst & Hardware list for the light detection library \\
less & A text file browser similar to more, \\
lesstif & A free Motif clone \\
lftp & Commandline ftp client. \\
libaa1 & AA (Ascii Art) library \\
libaa1-devel & Header files and libraries for developing apps \\
libadns1 & Advanced, easy to use, asynchronous-capable DNS client \\
libadns1-devel & Advanced, easy to use, asynchronous-capable DNS client \\
libao0-devel & Headers for developing programs that will use \\
libao0 & Main library for libao \\
libarts2-devel & Development files for arts \\
libarts2 & The libraries for arts \\
libaudiofile0-devel & Includes and other files to develop audiofile \\
libaudiofile0 & Main library for audiofile \\
libbinutils2-devel & Main library for binutils \\
libbinutils2 & Main library for binutils \\
libbonobo2-devel & Libraries and include files for the Bonobo \\
libbonobo2 & Libraries for Bonobo \\
libbzip2\_1-devel & Header files for developing apps which will \\
libbzip2\_1 & Libraries for developing apps which will use \\
libcdda0-devel & Development libraries for cdparanoia \\
libcdda0 & Libraries for cdparanoia \\
libcim3-devel & Headers for developing programs that will use \\
libcim3 & Gnu Cim libraries packages \\
libcups1 & Common Unix Printing System - CUPS library \\
libcups1-devel & Common Unix Printing System - Dev environment \\
libcurl1 & A library of functions for file transfer \\
libdetect0-devel & Header files and libraries for developing apps \\
libdetect0 & The detect library itself. Necessary to run \\
libdiffie1-devel & Static version of the diffie library \\
libdiffie1 & The diffie library, necessary to run mirrordir. \\
libefs1-devel & Embedded File System library \\
libefs1 & Embedded File System library \\
libesound0-devel & Includes and more to develop EsounD applications \\
libesound0 & Libraries for EsounD. \\
libext2fs2-devel & The librairies for Ext2fs \\
libext2fs2 & The librairies for Ext2fs \\
libfribidi0-devel & Library implementing the Unicode BiDi algorithm \\
libfribidi0 & Library implementing the Unicode BiDi algorithm \\
libgal4-devel & Libraries and include files for gal \\
libgal4 & Library for compound documents in GNOME \\
libGConf1-devel & Development libraries and headers for GConf \\
libGConf1 & GConf is a configuration database system. \\
libgd1 & A graphics library for generating .gif files \\
libgda0 & GNU Data Access \\
libgdbm1-devel & Development libraries and header files for the \\
libgdbm1 & Main library for gdbm \\
libghttp1-devel & GNOME http client development \\
libghttp1 & GNOME http client library. \\
libgimp1.2\_1-devel & GIMP plugin and extension development kit \\
libgimp1.2\_1 & GIMP libraries \\
libglade0-devel & Libraries, includes, etc to develop libglade applications \\
libglade0 & Libglade is a library that allows a \\
libglade-bonobo0 & Bonobo part of the libglade \\
libglade-gnome0 & GNOME part of the libglade \\
libglade-gnome-db0 & GNOME-DB part of the libglade \\
libglib1.2-devel & GIMP Toolkit and GIMP Drawing Kit support \\
libglib1.2 & Main library for glib \\
libgmp3 & A GNU arbitrary precision library \\
libgmp3-devel & Development tools for the GNU MP arbitrary \\
libgnome-db0-devel & GNOME DB Development \\
libgnome-db0 & GNOME DB libraries \\
libgnomeprint15-devel & Libraries and include files for developing GNOME \\
libgnomeprint15 & Libraries for Gnome-Print \\
libgnome-vfs0-devel & Libraries and include files for developing GNOME \\
libgnome-vfs0 & GNOME virtual file-system libraries \\
libgpm1-devel & Libraries and header files for developing mouse \\
libgpm1 & Libraries and header files for developing mouse \\
libgr1-devel & Development tools for programs which will use \\
libgr1 & Main library \\
libgr1-progs & Tools for manipulating graphics files in libgr \\
libgtk+1.2-devel & Development tools for GTK+ (GIMP ToolKit) apps. \\
libgtk+1.2 & Main library for gtk+ \\
libgtkglarea5 & GtkGLArea is an OpenGL widget for GTK+ \\
libgtkhtml7-devel & Development libraries, header files and utilities for \\
libgtkhtml7 & Libraries for GtkHTML \\
libgtkmm1.2-devel & Headers for developing programs that will use \\
libgtkmm1.2 & Main library for gtkmm \\
libgtkxmhtml1 & Libraries for gtkxmHTML \\
libgtop1-devel & Includes and other files to develop libgtop \\
libgtop1 & Main library for libgtop \\
libimlib1-devel & Includes and other files to develop imlib \\
libimlib1 & Main library for imlib \\
libisdn4k-utils2 & Main library for isdn4k-utils \\
libjabber1 & A jabber's librairies. \\
libjabber1-devel & Package to make developpement with libjabber. \\
libjpeg62 & A library for manipulating JPEG image format \\
libjpeg62-devel & Development tools for programs which will use \\
libjpeg-progs & Programs for manipulating JPEG format image files \\
liblcms1-devel & Header files and static library for development \\
liblcms1 & Little cms color engine \\
libldap1-devel & OpenLDAP development libraries and header files. \\
libldap1 & OpenLDAP libraries. \\
libldap2-devel & OpenLDAP development libraries and header files. \\
libldap2 & OpenLDAP libraries. \\
libltdl0-devel & Development files for libtool \\
libltdl0 & Shared library files for libtool \\
libmedusa0-devel & Libraries and include files for developing medusa \\
libmedusa0 & Medusa, the gnome search/indexing package \\
libmikmod2 & A portable sound library for Unix. \\
libmirrordirz1-devel & Static version of the mirrordirz library \\
libmirrordirz1 & The mirrordirz library, necessary to run mirrordir. \\
libmng1 & A library for handling MNG files \\
libmng1-devel & Static libraries and header file for libmng \\
libmorph0 & Internal library required for xmorph/gtkmorph \\
libncurses5-devel & The development files for applications which use \\
libncurses5 & The development files for applications which use \\
libnewt0.50-devel & Newt windowing toolkit development files. \\
libnewt0.50 & Newt windowing toolkit development files library. \\
liboaf0-devel & Development libraries and headers for OAF \\
liboaf0 & GNOME Object Activation Framework \\
libogg0-devel & Headers for developing programs that will use \\
libogg0 & Main library for libogg \\
libole20 & Libole2 library \\
libpcap0 & A system-indep interface for user-level packet capture \\
libpcap0-devel & Static library and header files for the \\
libpilot-link3 & Libraries needed to use pilot-link \\
libpng2 & A library of functions for manipulating PNG \\
libpng2-devel & Development tools for programs to manipulate PNG \\
libPropList-devel & Lib for configuration or preference files compatible \\
libPropList & Lib for configuration or preference files compatible \\
libpspell3-devel & Libraries, includes, and other files needed to \\
libpspell3 & Portable Spell Checker Interface Library \\
libpth1-devel & GNU Pth - GNU Portable Threads (Headers \\
libpth1 & GNU Pth - GNU Portable Threads. \\
libqt2-devel & Header files and libraries for developing apps \\
libqt2 & Shared library for the Qt2 GUI toolkit \\
libqtcups2-devel & QTCUPS library: provides Qt applications with support \\
libqtcups2 & Main library for QtCups \\
librep & An embeddable LISP environment \\
librep-devel & librep include files and link libraries \\
libsane1-devel & SANE - local and remote scanner access. \\
libsane1 & SANE - local and remote scanner access. \\
libsasl7 & Librairies for SASL a the Simple Authentication \\
libscrollkeeper0 & Libraries for scrollkeeper. \\
libSDL1.1-devel & Headers for developing programs that will use \\
libSDL1.1 & Main library for SDL \\
libSDL\_mixer1.1-devel & Headers for developing programs that will use \\
libSDL\_mixer1.1 & Main library for SDL\_mixer \\
libSDL\_mixer1.1-test & Test binary for SDL\_mixer \\
libsigc++1.0-devel & Headers for developing programs that will use \\
libsigc++1.0 & Main library for libsigc++ \\
libsigc++-examples & Examples and tests for the Typesafe Signal \\
libslang1-devel & The static library and header files for \\
libslang1 & The shared library for the S-Lang extension \\
libsmpeg0.4-devel & Headers for developing programs that will use \\
libsmpeg0.4 & Main library for smpeg \\
libstdc++2.10-devel & Header files and libraries for C++ development \\
libstdc++2.10 & GNU C++ library \\
libtabe0-devel & Header files and libraries for developing apps \\
libtabe0 & Libraries needed to use packages using libtabe \\
libtabe & Chinese lexicons library for xcin-2.5 \\
libtermcap2 & Development tools for programs which will access \\
libtiff3 & A library of functions for manipulating TIFF \\
libtiff3-devel & Development tools for programs which will use \\
libtiff3-progs & Binaries needed to manipulate TIFF format image \\
libtool & The GNU libtool, which simplifies the use \\
libungif4 & A library for manipulating GIF format image \\
libungif4-devel & Development tools for programs which will use \\
libunicode0-devel & A unicode manipulation library \\
libunicode0 & Unicode library \\
libunixODBC2 & unixODBC libraries \\
libvorbis0-devel & Headers for developing programs that will use \\
libvorbis0 & Main library for libvorbis \\
libwmf & A library to convert wmf files. \\
libwmf-devel & A library to convert wmf files. - \\
libXaw3d7 & A version of the MIT Athena widget \\
libXaw3d7-devel & Header files and static libraries for development \\
libxml-devel & Libraries, includes and other files to develop \\
libxml & The libXML library. \\
libxmms1-devel & Development package with static libs and headers \\
libxmms1 & Library associated with xmms, needed for xmms \\
libxode1 & A library for jabber. \\
libxode1-devel & Package to make developpement with libxode. \\
libxpm4 & A pixmap library for the X Window \\
libxpm4-devel & Tools for developing apps which will use \\
licq & ICQ clone written in C++, and the \\
lilo & The boot loader for Linux and other \\
links & Lynx-like text WWW browser \\
linuxconf & An extremely capable system configuration tool. \\
linuxconf-lang-cn & Chinese tranlation (simplified) \\
linuxconf-lang-cs & Czech translation \\
linuxconf-lang-de & Deutsch translation \\
linuxconf-lang-es & Spanish translation \\
linuxconf-lang-fi & Finish translation \\
linuxconf-lang-fr & French translation \\
linuxconf-lang-it & Italian translation \\
linuxconf-lang-ko & Korean(NeoCentury Systems Co.) translation \\
linuxconf-lang-no & Norsk translation \\
linuxconf-lang-pt & português - Brasil translation \\
linuxconf-lang-ro & Romanian translation \\
linuxconf-lang-ru-SU & Russian KOIS \\
linuxconf-lang-se & Swedish translation \\
linuxconf-lang-sk & Slovensky translation \\
linuxconf-lang-zh & Chinese tranlation (Traditional) \\
linuxconf-lib & Shared librairy providing the linuxconf UI toolkit \\
linuxconf-util & Various related utilities \\
linux\_logo & ASCII Tux (Linux Penguin) \\
lkmpg & The Linux Kernel Module Programming Guide \\
lm\_utils & Utilities for lm\_sensors. \\
locales-af & Base files for localization (Afrikaans) \\
locales-ar & Base files for localization (Arabic) \\
locales-az & Base files for localization (Azeri) \\
locales & Base files for localization \\
locales-be & Base files for localization (Belarussian) \\
locales-bg & Base files for localization (Bulgarian) \\
locales-br & Base files for localization (Breton) \\
locales-bs & Base files for localization (Bosnian) \\
locales-ca & Base files for localization (Catalan) \\
locales-cs & Base files for localization (Czech) \\
locales-cy & Base files for localization (Welsh) \\
locales-da & Base files for localization (Danish) \\
locales-de & Base files for localization (German) \\
locales-el & Base files for localization (Greek) \\
locales-en & Base files for localization (English) \\
locales-eo & Base files for localization (Esperanto) \\
locales-es & Base files for localization (Spanish) \\
locales-et & Base files for localization (Estonian) \\
locales-eu & Base files for localization (Basque) \\
locales-fa & Base files for localization (Farsi) \\
locales-fi & Base files for localization (Finnish) \\
locales-fo & Base files for localization (Faroese) \\
locales-fr & Base files for localization (French) \\
locales-ga & Base files for localization (Irish) \\
locales-gd & Base files for localization (Scottish Gaelic) \\
locales-gl & Base files for localization (Galician) \\
locales-gv & Base files for localization (Manx Gaelic) \\
locales-he & Base files for localization (Hebrew) \\
locales-hi & Base files for localization (Hindi) \\
locales-hr & Base files for localization (Croatian) \\
locales-hu & Base files for localization (Hungarian) \\
locales-hy & Base files for localization (Armenian) \\
locales-id & Base files for localization (Indonesian) \\
locales-is & Base files for localization (Icelandic) \\
locales-it & Base files for localization (Italian) \\
locales-ja & Base files for localization (Japanese) \\
locales-ka & Base files for localization (Georgian) \\
locales-kl & Base files for localization (Greenlandic) \\
locales-ko & Base files for localization (Korean) \\
locales-kw & Base files for localization (Cornish) \\
locales-lo & \\
locales-lt & Base files for localization (Lithuanian) \\
locales-lv & Base files for localization (Latvian) \\
locales-mi & Base files for localization (Maori) \\
locales-mk & Base files for localization (Macedonian) \\
locales-ms & Base files for localization (Malay) \\
locales-nl & Base files for localization (Dutch) \\
locales-no & Base files for localization (Norwegian) \\
locales-oc & Base files for localization (Occitan) \\
locales-pd & Base files for localization (Plautdietsch) \\
locales-ph & Base files for localization (Pilipino) \\
locales-pl & Base files for localization (Polish) \\
locales-pp & Base files for localization (Papiamento) \\
locales-pt & Base files for localization (Portuguese) \\
locales-ro & Base files for localization (Romanian) \\
locales-ru & Base files for localization (Russian) \\
locales-sk & Base files for localization (Slovak) \\
locales-sl & Base files for localization (Slovenian) \\
locales-sq & Base files for localization (Albanian) \\
locales-sr & Base files for localization (Serbian) \\
locales-sv & Base files for localization (Swedish) \\
locales-ta & Base files for localization (Tamil) \\
locales-tg & Base files for localization (Tajik) \\
locales-th & Base files for localization (Thai) \\
locales-tr & Base files for localization (Turkish) \\
locales-tt & Base files for localization (Tatar) \\
locales-uk & Base files for localization (Ukrainian) \\
locales-ur & Base files for localization (Urdu) \\
locales-uz & Base files for localization (Uzbek) \\
locales-vi & Base files for localization (Vietnamese) \\
locales-wa & Base files for localization (Walloon) \\
locales-yi & Base files for localization (Yiddish) \\
locales-zh & Base files for localization (Chinese) \\
logrotate & Rotates, compresses, and mails system logs \\
losetup & Programs for setting up and configuring loopback \\
lpg & The LDP's Linux programming guide in HTML \\
lpr & A utility that manages print jobs. \\
lslk & A lock file lister. \\
lsof & Lists files open by processes \\
lvm & Logical Volume Manager administration tools \\
lynx & Text based browser for the world wide \\
m4 & The GNU macro processor. \\
mailcap & Associates helper applications with particular file types. \\
mailx & The /bin/mail program, which is used to \\
make & A GNU tool which simplifies the build \\
MAKEDEV & A program used for creating the device \\
man & A set of documentation tools: man, apropos \\
mandrake\_desk & The Desktop configuration files for Linux Mandrake \\
mandrake\_doc-en & The Linux-Mandrake Installation Guide and User Guide, \\
mandrake-release & Linux Mandrake release file \\
man-pages-de & German man (manual) pages from the Linux \\
man-pages-es & Spanish man (manual) pages from the Linux \\
man-pages-fr & French man (manual) pages from the Linux \\
man-pages-hu & Hungarian manual pages \\
man-pages-id & Man pages in Indonesian language \\
man-pages-it & Italian manual pages \\
man-pages-ko & Korean(Hangul) Man Pages \\
man-pages & Man (manual) pages from the Linux Documentation \\
man-pages-pl & Man pages in polish language \\
man-pages-ru & Russian man (manual) pages from the Linux \\
man-pages-zh & Chinese Man Pages \\
mawk & An interpreter for the awk programming language \\
mc & A user-friendly file manager and visual shell \\
medusa & Medusa, the gnome search/indexing package \\
memprof & Tool for memory profiling and leak detection \\
menudrake & Menudrake is a little application for editing \\
menu & Menu system \\
Mesa-common & Files for Mesa (GLU and glut libs) \\
Mesa-demos & Demos for Mesa (OpenGL compatible 3D lib) \\
Mesa & OpenGL 1.2 compatible 3D graphics library \\
metamail & A program for handling multimedia mail using \\
mgetty & A getty replacement for use with data \\
mgetty-sendfax & Provides support for sending faxes over a \\
mgetty-viewfax & An X Window System fax viewer. \\
mgetty-voice & A program for using your modem and \\
mikmod & A MOD music file player. \\
mingetty & A compact getty program for virtual consoles \\
minicom & A text-based modem control and terminal emulation \\
mirrordir & Easy to use ftp mirroring package \\
mkbootdisk & Creates a bootdisk. \\
mkinitrd & Creates an initial ramdisk image for preloading \\
mkisofs & Creates an image of an ISO9660 filesystem. \\
mktemp & A small utility for safely making /tmp \\
mkxauth & A utility for managing .Xauthority files. \\
mm & Shared Memory Abstraction Library \\
mod\_perl-common & The mod\_perl and apache-mod\_perl common files \\
mod\_perl-devel & Apache-Mod\_Perl Development Files \\
mod\_php & The PHP4 HTML-embedded scripting language for use \\
mod\_ssl & An SSL module for the Apache Web \\
modutils & The kernel daemon (kerneld) and kernel module \\
mount & Programs for mounting and unmounting filesystems. \\
mozilla-fonts & A set fonts for Netscape and Mozilla \\
mozilla & Mozilla, open-source web browser \\
mozilla-psm & SSL support for Mozilla. \\
mp3info & Mp3info - Utility for MP3 information and \\
mpage & A tool for printing multiple pages of \\
mpeg\_lib & Mpeg library \\
mpg123 & MPEG audio player \\
msec & Security Level \& Program for the Linux \\
mtools & Programs for accessing MS-DOS disks without mounting \\
mt-st & Programs to control tape device operations. \\
mutt & A text mode mail user agent. \\
nag & The Linux Doc Project's Network Administrators' Guide \\
nautilus-mozilla & Nautilus component for use with Mozilla \\
nautilus & Nautilus is a file manager for the \\
ncompress & Fast compression and decompression utilities. \\
ncpfs & Utilities for the ncpfs filesystem, a NetWare \\
ncurses & A CRT screen handling and optimization package \\
netscape-chinese\_big5 & Netscape in simplified Chinese \\
netscape-chinese\_gb2312 & Netscape in simplified Chinese \\
netscape-common & Files shared by the Netscape Navigator and \\
netscape-communicator & Netscape tools, including a Web browser, news \\
netscape-francais & Netscape in french \\
netscape-german & Netscape in German \\
netscape-plugins & Flash plugin (version 4) for Netscape \\
net-tools & The basic tools for setting up networking. \\
newt & A development library for text mode user \\
nfs-utils-clients & The utilities for Linux NFS client. \\
nfs-utils & The utilities for Linux NFS server. \\
nmap-frontend & Gtk+ frontend for nmap \\
nmap & Network exploration tool and security scanner \\
nss\_ldap & NSS library and PAM module for LDAP. \\
ntsysv & A system tool for maintaining the /etc/rc0.d, \ldots \\
numlock & Numlock key locker \\
open & A tool which will start a program \\
openjade & Jade and SP -- parser and tools \\
openldap & LDAP servers and sample clients. \\
openssh-askpass-gnome & OpenSSH GNOME passphrase dialog \\
openssh-askpass & OpenSSH X11 passphrase dialog \\
openssh-clients & OpenSSH Secure Shell protocol clients \\
openssh & OpenSSH free Secure Shell (SSH) implementation \\
openssh-server & OpenSSH Secure Shell protocol server (sshd) \\
openssl-devel & Secure Sockets Layer communications static libs \& \\
openssl & Secure Sockets Layer communications libs \& utils \\
ORBit-devel & Development libraries, header files and utilities for \\
ORBit & High-performance CORBA Object Request Broker. \\
pam & A security tool which provides authentication for \\
pam-devel & Development headers and libraries for pam \\
pango & System for layout and rendering of internationalized \\
passwd & The passwd utility for setting/changing passwords using \\
patch & The GNU patch command, for modifying/upgrading files. \\
pciutils & Linux PCI utilities. \\
perl-base & The Perl programming language (base). \\
perl-CGI & Simple Common Gateway Interface class for Perl. \\
perl-Curses & Perl module for character screen handling and \\
perl-Data-ShowTable & Perl 5 module to print arrays of \\
perl-DB\_File & Perl module for use of the Berkeley \\
perl-DBI & The Perl Database Interface by Tim Bunce \\
perl-devel & The Perl programming language (devel). \\
perl-Digest-MD5 & Digest-MD5 mod for perl (Sec\_and\_Encryp/SHA) \\
perl-gettext & Gettext routines for Perl. \\
perl-GTK-GdkImlib & Perl module for the gtk+ GdkImlib library. \\
perl-GTK-GdkPixbuf & Perl module for the gtk+ GdkPixbuf library. \\
perl-GTK-Glade & Perl module for the gtk+ Glade library. \\
perl-GTK-GLArea & Perl module for the gtk+ GLArea library. \\
perl-GTK-Gnome & Perl module for the gtk+ Gnome library. \\
perl-GTK & Perl module for the gtk+ library. \\
perl-HTML-Parser & HTML-Parser mod for perl (WWW.CGI,HTML,\ldots) \\
perl-HTML-SimpleParse & HTML-SimpleParse mod for perl (WWW,CGI,HTML,\ldots) \\
perl-IO-stringy & Perl module for I/O on in-core objects \\
perl-libnet & Libnet module for perl (Networking\_Devices\_IPC/Net) \\
perl-libwww-perl & Libwww-perl module for perl \\
perl-Magick & Libraries and modules for access to ImageMagick \\
perl-MailTools & This is MailTools, a set of perl \\
perl-MIME-Base64 & Perl module for MIME encoding/decoding (base64 and \\
perl-MIME-tools & Perl modules for parsing (and creating!) MIME \\
perl-Msgcat & Msgcat, a small Perl module for XPG4 \\
perl-Net\_SSLeay & Net::SSLeay (module for perl) \\
perl-PDL & PerlDL, an efficient numerical language for scientific \\
perl-RPM & Perl-RPM - Native bindings to the RPM \\
perl-Term-Readline-Gnu & Implementation of Internet protocols for Perl \\
perl & The Perl programming language. \\
perl-Tk & Tk modules for Perl \\
perl-URI & URI mod for perl  (WWW,CGI,HTML,\ldots) \\
php-common & Shared library for php \\
php & The PHP4 scripting language \\
pidentd & An implementation of the RFC1413 identification server. \\
pilot-link & File transfer utilities between Linux and PalmPilots \\
pinfo & Przemek's Info Viewer - a (much) better \\
playmidi & A MIDI sound file player. \\
playmidi-X11 & An X Window System based MIDI sound \\
pmake-customs & A remote execution facility for pmake. \\
pmake & The BSD 4.4 version of make. \\
popt & A C library for parsing command line \\
popt-devel & A C library for parsing command line \\
portmap & A program which manages RPC connections \\
postfix & Postfix Mail Transport Agent \\
postgresql-odbc & The ODBC driver needed for accessing a \\
postgresql-perl & Development module needed for Perl code to \\
postgresql & PostgreSQL client programs and libraries. \\
postgresql-python & Development module for Python code to access \\
postgresql-server & The programs needed to create and run \\
ppp & The PPP daemon and documentation for Linux \\
pptp-adsl-fr & PPTP-linux VPN client ( Alcatel ADSL Modem \\
pptp-client & PPTP-linux VPN client \\
procinfo & A tool for gathering and displaying system \\
procmail & The procmail mail processing program. \\
procps-devel & An X based system message monitoring utility \\
procps & Utilities for monitoring your system and processes \\
procps-X11 & An X based system message monitoring utility \\
proftpd & ProFTPd -- Professional FTP Server. \\
psacct & Utilities for monitoring process activities. \\
psmisc & Utilities for managing processes on your system. \\
psutils & PostScript utilities \\
pump & A Bootp and DHCP client for automatic \\
pwdb & The password database library. \\
pygtk & Python bindings for the GTK+ widget set \\
python & An interpreted, interactive object-oriented prog lang \\
python-devel & The libraries and header files needed for \\
pythonlib & library of python code used by various \\
python-numeric & Python numerical facilities \\
qiv & Gdk/imlib image viewer \\
qt2-designer & Interface designer (IDE) for the Qt toolkit \\
qt2-Xt & An Xt (X Toolkit) compatibility add-on for \\
qtcups & A CUPS interface and library for Qt \\
queso & OS identification program \\
quota & System administration tools for monitoring users' disk \\
raidtools & Tools for creating and maintaining software RAID \\
rcs & Revision Control System (RCS) file version management \\
rdate & Retrieving the date and time from another \\
rdist & Maintains identical copies of files on multiple \\
readline-devel & file for developing programs that use the \\
readline & Library for reading lines from a terminal \\
recode & GNU recode \\
reiserfsprogs & The utilities to create Reiserfs volume. \\
rep-gtk-gnome & GNOME binding for librep \\
rep-gtk & GTK+ binding for librep Lisp environment \\
rgrep & A grep utility which can recursively descend \\
rhs-printfilters & Red Hat print filters, for use with \\
rio500 & Rio 500 Support \\
rmt & Provides certain programs with access to remote \\
rootfiles & The basic required files for the root \\
routed & The routing daemon which maintains routing tables. \\
rpm-build & Scripts and executable programs used to build \\
rpm-devel & Development files for applications which will manipulate \\
rpmdrake & A graphical front end for installing packages \\
rpmlint & Rpm correctness checker \\
rpm-python & Python bindings for apps which will manipulate \\
rpmstats & Gather statistics from installed packages \\
rpm & The RPM package management system \\
rpmtools & Contains various rpm command-line tools \\
rp-pppoe & ADSL/PPPoE userspace driver \\
rrdtool & RRDtool - round robin database \\
rsh & Clients for remote access commands (rsh, rlogin, \\
rsh-server & Servers for remote access commands (rsh, rlogin, \\
rsync & A program for synchronizing files over a \\
rusers & Displays the users logged into machines on \\
rwall & Client and server for sending messages to \\
rwho & Displays who is logged in to local \\
rxvt & A color VT102 terminal emulator for the \\
rxvt-CJK & CJK menus for rxvt. \\
sag & The LDP's System Administrators' Guide in HTML \\
samba-client & Samba (SMB) client programs. \\
samba-common & Files used by both Samba servers and \\
samba & Samba SMB server. \\
sane-backends & SANE - local and remote scanner access. \\
sane-frontends & Graphical frontend to SANE \\
sane & SANE - local and remote scanner access. \\
sash & A statically linked shell, including some built-in \\
sawfish & An extensible window manager for the X \\
sawfish-themes & A collection of themes for the sawfish \\
screen & A screen manager that supports multiple logins \\
scrollkeeper & ScrollKeeper is a cataloging system for documentation \\
sed & A GNU stream text editor. \\
sendmail & A widely used Mail Transport Agent (MTA) \\
setserial & A utility for configuring serial ports \\
setup & A set of system configuration and setup \\
sfio & A Safe/Fast I/O Library \\
sfio-devel & Libraries, includes and other files for Safe/Fast \\
sgml-common & Base ISO character entities and utilities for \\
sgml-tools & A text formatting package based on SGML \\
shadow-utils & Utilities for managing shadow password files and \\
sharutils & The GNU shar utilities for packaging and \\
sh-utils & A set of GNU utilities commonly used \\
slocate & Finds files on a system via a \\
slrn & A powerful, easy to use, threaded Internet \\
sox & A general purpose sound file conversion tool. \\
spec-helper & Tools to ease the creation of rpm \\
squid & The Squid proxy caching server. \\
stat & A tool for finding out information about \\
strace & Tracks and displays system calls associated with \\
sudo & Allows command execution as root for specified \\
symlinks & A utility which maintains a system's symbolic \\
sysklogd & System logging and kernel message trapping daemons. \\
SysVinit & Programs which control basic system processes. \\
t1lib1-progs & Programs dor manipulating Type 1 font \\
t1lib1 & Type 1 font rasterizer \\
talk & Talk client for one-on-one Internet chatting. \\
taper & A menu-driven file backup system. \\
tar & A GNU file archiving program. \\
tcl & An embeddable scripting language. \\
tcpdump & A network traffic monitoring tool. \\
tcp\_wrappers & A security tool which acts as a \\
tcsh & An enhanced version of csh, the C \\
telnet & Client for the telnet remote login protocol. \\
telnet-server & Server for the telnet remote login protocol. \\
termcap & The terminal feature database used by certain \\
texinfo & Tools needed to create Texinfo format documentation \\
textutils & A set of GNU text file modifying \\
tftp & The client and server for the Trivial \\
time & A GNU utility for monitoring a program's \\
timeconfig & Text mode tools for setting system time \\
tin & A basic Internet news reader. \\
tmake & Easy-to-use tool for creating and maintaining portable \\
tmpwatch & A utility for removing files based on \\
traceroute & Traces the route taken by packets over \\
transfig & A utility for converting FIG files (made \\
tree & A utility which displays a tree view \\
trn & A news reader that displays postings in \\
tuxracer & Tux Racer \\
ucd-snmp & A collection of SNMP protocol tools from \\
ucd-snmp-utils & Network management utilities using SNMP, from the \\
umb-scheme & An implementation of the Scheme programming language \\
unarj & An uncompressor for .arj format archive files. \\
unixODBC & Unix ODBC driver manager and database drivers \\
unzip & Unpacks ZIP files such as those made \\
urlview & A URL extractor/viewer for use with Mutt. \\
urpmi & User mode rpm install \\
urw-fonts & Free versions of the 35 standard PostScript \\
usbd & Linux USB daemons autoloader. \\
usbutils & Linux USB utilities \\
usbview & USB topology and device viewer \\
userdrake & Tool to edit the user/group base on \\
usermode & Graphical tools for certain user account management \\
utempter-devel & devel for utempter \\
utempter & Privledged helper for utmp/wtmp updates \\
util-linux & A collection of basic system utilities \\
uucp & The uucp utility for copying files between \\
uxcook & Fix problems resulting of improperly set FTP \\
vdk-devel & The Visual Development Kit is a C++ \\
vim-common & The common files needed by any version \\
vim-enhanced & A version of the VIM editor which \\
vim-minimal & A minimal version of the VIM editor. \\
vim-X11 & The VIM version of the vi editor \\
vixie-cron & The Vixie cron daemon for executing specified \\
vlock & A program which locks one or more \\
vorbis-tools & Several Ogg Vorbis Tools \\
webmin & An SSL web-based administration interface for Unix \\
wget & A utility for retrieving files using the \\
which & Displays where a particular program in your \\
words & A dictionary of English words for the \\
wv & MSWord 6/7/8/9 binary file format -> HTML \\
xa+cv & XCIN ANYWHERE +CV by weijr and Platin \\
xalf & A utility to provide feedback when starting \\
xawtv & Video4Linux Stream Capture Viewer \\
xchat & Graphical IRC client \\
xcin & A X Input Method Server for Chinese \\
xcpustate & An X Window System based CPU state \\
xdaliclock & A clock for the X Window System. \\
xdelta & A binary delta generator \\
xerces-c & XML parser \\
xfig & An X Window System tool for drawing \\
XFree86-100dpi-fonts & X Window System 100dpi fonts. \\
XFree86-3DLabs & XFree86 3DLabs server. \\
XFree86-75dpi-fonts & A set of 75 dpi resolution fonts \\
XFree86-8514 & The XFree86 server program for older IBM \\
XFree86-AGX & The XFree86 server for AGX-based video cards. \\
XFree86-cyrillic-fonts & Cyrillic fonts - only needed on the \\
XFree86-devel & Headers and programming man pages. \\
XFree86-FBDev & The X server for the generic frame \\
XFree86-glide-module & The glide module for XFree86 server. \\
XFree86-I128 & The XFree86 server for \#9 Imagine 128 \\
XFree86-ISO8859-2-100dpi-fonts & ISO 8859-2 fonts in 100 dpi resolution \\
XFree86-ISO8859-2-75dpi-fonts & A set of 75 dpi Central European \\
XFree86-ISO8859-2 & Central European language fonts for the X \\
XFree86-ISO8859-2-Type1-fonts & Type 1 scalable Central European language (ISO8859-2) \\
XFree86-ISO8859-9-100dpi-fonts & 100 dpi Turkish (ISO8859-9) fonts for X. \\
XFree86-ISO8859-9-75dpi-fonts & 75 dpi Turkish (ISO8859-9) fonts for X. \\
XFree86-ISO8859-9 & Turkish language fonts and modmaps for X. \\
XFree86-libs & Shared libraries needed by the X Window \\
XFree86-Mach32 & The XFree86 server for Mach32 based video \\
XFree86-Mach64 & The XFree86 server for Mach64 based video \\
XFree86-Mach8 & The XFree86 server for Mach8 video cards. \\
XFree86-Mono & A generic XFree86 monochrome server for VGA \\
XFree86-P9000 & The XFree86 server for P9000 cards. \\
XFree86 & Part of the XFree86 implementation of the \\
XFree86-S3 & The XFree86 server for video cards based \\
XFree86-S3V & The XFree86 server for video cards based \\
XFree86-server-common & Font library. \\
XFree86-server & The X server and associated modules \\
XFree86-SVGA & An XFree86 server for most simple framebuffer \\
XFree86-VGA16 & A generic XFree86 server for VGA16 boards. \\
XFree86-W32 & The XFree86 server for video cards based \\
XFree86-xfs & Font server for XFree86 \\
XFree86-Xnest & A nested XFree86 server. \\
xinetd & Xinetd is a powerful replacement for inetd. \\
xinitrc & The default startup script for the X \\
xkobo & X11 space arcade game \\
xli & XLI - X11 Image Loading Utility \\
xlockmore & An X terminal locking program. \\
xmailbox & An X Window System utility which notifies \\
xml-common & Common XML catalog and DTD files \\
xmms-arts & KDE aRtsd output plugin for XMMS. \\
xmms-esd & ESound output backend \\
xmms-gnome & Gnome applet for XMMS \\
xmms-mikmod & Sound player with the WinAmp GUI, Mikmod \\
xmms-skins & XMMS - Skins \\
xmms-smpeg & This plugin lets you play mpeg videos \\
xmms & The Sound player with the WinAmp GUI \\
xmorph & An X Window System tool for creating \\
xmovie & A movie player for QuickTime and MPEG-2 \\
xpdf & A PDF file viewer for the X \\
xpp & X Printing Panel \\
xscreensaver & A set of X Window System screensavers \\
xterm & A terminal emulator for the X Window \\
xwpick & An X Window System screenshot grabber \\
ypbind & The NIS daemon which binds NIS clients \\
ypserv & The NIS (Network Information Service) server \\
yp-tools & NIS (or YP) client programs. \\
ytalk & A chat program. \\
zh-autoconvert & Chinese HZ/GB/BIG5 encodings auto-converter \\
zh-autoconvert-devel & Header files and libraries for developing apps \\
zh-autoconvert-xchat & zh Auto-convert xchat plugins \\
zip & A file compression and packaging utility compatible \\
zlib1-devel & Header files and libraries for developing apps \\
zlib1 & The zlib compression and decompression library \\
zsh & A shell with lots of features. \\
7colors & Little addicting game, take over the gaming \\
abisuite & Lean and fast full-featured word processor \\
alsa-lib-devel & Devel file for Advanced Linux Sound Architecture \\
alsaplayer & Advanced Linux Sound Architecture (ALSA) player \\
ami-gnome & Korean IMS AMI, GNOME Applet mode \\
ami & Korean IMS Ami \\
anonftp & A program which enables anonymous FTP access. \\
Apache-ASP & Apache-ASP module for perl \\
apache-devel & Module development tools for the Apache web \\
apache-manual & Apache Manual \\
apcupsd & Power management software for APC UPS hardware \\
apmd-devel & The development librairies for APM. \\
app-defaults-uk & X Resources for ukrainization of some applications \\
auctex & Enhanced LaTeX mode for GNU Emacs \\
autoirpm & Auto install of rpm on demand \\
AVLTree-devel & AVL Tree library \\
bash1 & The GNU Bourne Again shell (bash) \\
bash-doc & Documentation for the GNU Bourne Again shell \\
bcast & Non-linear production environment for audio and video \\
bg5ps & A program for converting PostScript files to \\
bind-devel & Include files and libraries needed for bind \\
BitchX & Textmode IRC client \\
blt & A Tk toolkit extension, including widgets, geometry \\
bluefish & A WYSIWYG GPLized HTML editor \\
boa & The boa web server \\
bobobot & Mario-like game \\
bonnie & Unix filesystem performance benchmark \\
bronc & Bronc - Flexible front end to RRD-tool \\
bugsquish & Kill bugs with mouse \\
bumprace & Drive the ship to exit \\
bzflag & A multiplayer 3D tank battle game \\
cdlabelgen & Program for generating frontcards and traycards for \\
cdrecord-devel & The libschily SCSI user level transport library \\
cervisia & A kde graphical frontend to CVS \\
cfengine & Cfengine helps administer remote BSD and System-5-like \\
circuslinux & Cute breakout-like \\
clanbomber & Clanbomber - (GPL) Bomberman-like multiplayer game \\
clanlib-docs & ClanLib documentation \\
clips & Clips language for expert systems \\
compat-glibc & GNU libc for Linux-Mandrake 7.2 backwards compatibility \\
comsat & A mail checker client and comsat mail \\
console-tools-devel & devel for linux console tools \\
control-center-devel & GNOME control-center development files. \\
cooledit & Full featured multiple window programmer's text editor \\
cracklib-devel & cracklib link library \& header file \\
csmash & CannonSmash, a 3D tabletennis game \\
curl & Gets a file from a FTP, GOPHER \\
cvsweb & Visual (www) interface to explore a cvs \\
cxhextris & An X Window System color version of \\
db1-devel & Development libs/header files for Berkeley DB (version \\
db2-devel & Development libs/header files for Berkeley DB (version \\
db3-utils & Command line tools for managing Berkeley DB \\
defendguin & Defender clone \\
dev86-devel & A development files for dev86 \\
dmalloc & Debugging MALLOC \\
docbook-dtd31-sgml & SGML document type definition for DocBook 3.1. \\
docbook-style-dsssl-doc & Documentation for DocBook stylesheets \\
docbook-style-xsl & Norman Walsh\'s modular stylesheets for DocBook. \\
docbook-utils & Shell scripts to manage DocBook documents. \\
dosemu & A DOS emulator. \\
dosemu-freedos & A FreeDOS hdimage for dosemu, a DOS \\
doxygen & Doxygen is THE documentation system for C/C++ \\
dpsftp & DPS-FTP is a powerful FTP client for \\
egcs-c++ & C++ support for the gcc compiler \\
egcs-g77 & Fortran 77 support for the gcc compiler \\
egcs-objc-devel & Objective C support for the gcc compiler \\
egcs-objc & Objective C support for the gcc compiler \\
eggdrop & Eggdrop is an IRC bot, written in \\
ElectricFence & A debugger which detects memory allocation violations \\
emacs-el & The sources for elisp programs included with \\
emacs-pcomplete & Programmable completion for Emacs \\
emacs-tramp & Transparent Remote (file) Access, Multiple Protocol \\
eMusic & Sound player for the Enlightenment window-manager. \\
enlightenment-conf & Enlightenment Configuration applet \\
enlightenment & The Enlightenment window manager \\
eog & The Eye of GNOME image viewer \\
Epplets & applets for enlightenment \\
eroaster & The ECLIPT Roaster is a graphical frontend \\
eshell-emacs & An Emacs command shell \\
eshell-xemacs & An XEmacs command shell \\
Eterm-devel & Devel files for Eterm \\
Eterm & Eterm Enlightened Terminal Emulator for X Window \\
ethemes & Themes for Enlightenment \\
ethtool & Ethernet settings tool for network cards \\
evolution-devel & Libraries and include files for developing Evolution \\
exmh & The exmh mail handling system. \\
expect & A tcl extension for simplifying program-script interaction. \\
faces-devel & The Faces program's library and header files. \\
faces-xface & Utilities needed by mailers for handling Faces' \\
FaxMail & A program to send faxes for free \\
fdutils & Programs for dealing with floppy disks \\
fetchmailconf & A utility for graphically configuring your fetchmail \\
fetchmail-daemon & SySV init script for demonize fetchmail for \\
FileRunner & A simple file manager with built-in FTP \\
finger-server & The finger daemon. \\
fonts-hebrew-elmar & Hebrew Fonts by Eli Marmor \\
fonts-ttf-armenian & Free Armenian TrueType fonts \\
fonts-ttf-big5 & Chinese (Big5) TTF fonts \\
fonts-ttf-decoratives & free True Type Fonts (decoratives) \\
fonts-ttf-gb2312 & Chinese (GB2312) TTF fonts \\
fonts-ttf-japanese & Free Japanese TrueType fonts (mincho \& gothic) \\
fonts-ttf-korean & Baekmuk korean fonts \\
fonts-ttf-thai & Free Thai TrueType fonts \\
fonts-ttf-west\_european & free True Type Fonts (west eruopean charset) \\
fonts-type1-baltic & Type1 fonts in iso-8859-13 encoding \\
fpc & Free Pascal Compiler \\
freeciv & FREE CIVilization clone \\
freetype2-devel & Header files and static library for development \\
freetype-devel & Header files and static library for development \\
FreeWnn-devel & development library and header file for Wnn \\
FreeWnn & Japanese Input System \\
fvwm2 & An improved version of the FVWM X-based \\
fvwm2-icons & Graphic files used by the FVWM and \\
fvwm & An X Window System based window manager \\
galeon & Gnome browser based on Gecko (Mozilla) \\
gatos & ATI TV Tuner/Drivers \\
gawk-doc & Documentation about the GNU version of the \\
gcc-doc & Gcc documentation \\
gcc-java & Java support for gcc \\
gcombust & Gcombust is a burning cd frontend \\
gda & GNU Data Access \\
gda-mysql0 & GDA MySQL Provider \\
gdk-pixbuf-devel & Development tools for GdkPixBuf applications. \\
gedit-devel & Libraries needed to develop plugins for gedit \\
gemdropx & Tetris meets Space Invaders \\
genromfs & Tool for creating romfs filesystems. \\
gettext-devel & GNU libraries and utilities for producing multi-lingual \\
gfcc & GTK+ Firewall Control Center \\
ggv & The GNOME system monitor. \\
gif2png & tools for converting websites from using GIFs \\
gimp-data-extras & The GNU Image Manipulation Program \\
gimp-perl & GIMP perl extensions and plugins \\
git & A set of GNU Interactive Tools. \\
gkrellm-devel & gkrellm include files \\
gkrellm & Multiple stacked system monitors: 1 process. \\
glade & Gtk/gnome widget builder \\
glademm & A module for make gtkmm program with \\
Glide\_V2-devel & Development libraries for Glide 2.x \\
Glide\_V3-devel & Development libraries for Glide 2.x \\
Glide\_V3-DRI-devel & Development headers for Glide 3.x \\
Glide\_V5-devel & Development headers for Glide 3.x \\
gnome-audio-extra & Optional Sounds for GNOME events. \\
gnome-core-devel & GNOME core libraries, includes and more \\
gnome-db & GNOME DB \\
gnome-games-devel & GNOME games development libraries \\
gnome-games & GNOME games \\
gnome-guile-devel & GNOME guile libraries, includes, etc \\
gnome-guile & GNOME guile interpreter \\
gnomemm-devel & Headers for developing programs that will use \\
gnome-objc-devel & Libraries, includes and other files to develop \\
gnome-pilot-conduits & Gnome-pilot conduits \\
gnome-pilot-devel & GNOME pilot libraries, includes, etc \\
gnome-pim-conduits & Gnome Pilot conduits for GnomeCal and GnomeCard \\
gnome-pim-devel & GNOME PIM development files \\
gnome-spell & Gnome Spell is GNOME/Bonobo component for spell \\
gnome-telnet & A pretty frontend and easy to use \\
gnome-user-docs & GNOME User Documentation \\
gnome-users-guide & The GNOME Users' Guide \\
gnucash-devel & Libraries needed to develop for gnucash \\
gnucash & GnuCash is an application to keep track \\
gnuchess & The GNU chess program. \\
gnumeric-devel & Files necessary to develop gnumeric-based applications. \\
gnuplot & A program for plotting mathematical expressions and \\
gnus-doc & Gnus Newsreader for XEmacs \\
gob & GOB, The GTK+ Object Builder \\
gperf & A perfect hash function generator \\
gprolog & GNU Prolog is a free Prolog \\
gps & Another task manager applet \\
gqcam & A Linux clone of the QuickPict software \\
groff-gxditview & An X previewer for groff text processor \\
groff-perl & Parts of the groff formatting system that \\
grub-doc & More doc for grub \\
gsl & The GNU Scientific Library for numerical analysis. \\
gtkeyboard & Graphical Keyboard \\
gtkgraph & Simple GTK graphing calculator \\
gtk+licq-base & base files for gtk+licq \\
gtk+licq & gtk+licq is a gtk based GUI plugin \\
gtk+licq-nognome & gtk+licq without gnome support \\
gtk+mdk-devel & Mandrake specific GTK+ Widgets \\
gtktalog & The Gnome disk catalog. \\
gtk-themes & Themes for GTK \\
gtkzip & A program for maintaining your Zip drive \\
gtm-applet & GNOME applets for gtm \\
gtm & GNOME TransferManager allows the user to retrieve \\
gtulpas & Gnome Tulpas is a pool game \\
guile-devel & The libraries and header files for the \\
g-wrap & A utility for automatically generating glue code \\
g-wrap-devel & Header files and static libs for g-wrap \\
HDF & Hierarchical Data Format Library \\
HDF-util & HDF utilities and test data files \\
heartbeat & Heartbeat - subsystem for High-Availability Linux \\
heroes & Game like Nibbles but different. \\
howto-html-de & HOWTO documents (html format) from the Linux \\
howto-html-es & HOWTO documents (html format) from the Linux \\
howto-html-fr & HOWTO documents (html format) from the Linux \\
howto-html-it & Italian HOWTO documents (html format) from the \\
howto-html-ja & Japanese HOWTO documents (html format) from the \\
howto-html-zh & Chinese HOWTO documents (html format) from the \\
HTML-Embperl & HTML::Embperl module \\
HTML-Mason & HTML-Mason - Powerful Perl-based web site development \\
hugs98 & Hugs 98: The Nottingham and Yale Haskell \\
hylafax-client & The files for the HylaFAX(tm) fax client. \\
hylafax & HylaFAX(tm) is a sophisticated enterprise strength fax \\
hylafax-server & The files for the HylaFAX(tm) fax server. \\
ical & An X Window System-based calendar program \\
icebreaker & An action-puzzle game involving bouncing penguins \\
ifrac & 3D tetris \\
ImageMagick-devel & Static libraries and header files for ImageMagick \\
imap-devel & Libraries, includes, etc to develop IMAP applications \\
inews & Sends Usenet articles to a local news \\
inn-devel & The INN (InterNetNews) library. \\
iplog & Logs TCP, UDP, and ICMP connections to \\
iptables-ipv6 & IPv6 support for iptables \\
ipvsadm & Administration tool for Linux Virtual Server \\
irda-utils & Utilities for infrared communication between devices \\
isapnptools-devel & Devel librairies for configuring ISA Plug-and-Play (PnP) \\
ispell-af & Afrikaans files for ispell \\
ispell-br & Breton files for ispell \\
ispell-ca & Catalan files for ispell \\
ispell-da & Danish files for ispell \\
ispell-el & Greek files for ispell \\
ispell-eo & Esperanto files for ispell \\
ispell-fi & Finnish files for ispell \\
ispell-ga & Irish files for ispell \\
ispell-gd & Scottish files for ispell \\
ispell-gv & Manx Gaelic files for ispell \\
ispell-id & Indonesian files for ispell \\
ispell-nl & Dutch files for ispell \\
ispell-no & Norwegian files for ispell \\
ispell-pl & Polish files for ispell \\
ispell-pt\_BR & Brazilian Portuguese files for ispell \\
ispell-pt & Portuguese files for ispell \\
ispell-ro & Romanian files for ispell \\
ispell-ru & Russian files for ispell \\
ispell-sk & Slovak files for ispell \\
ispell-sl & Slovenian files for ispell \\
ispell-sv & Swedish files for ispell \\
itcl & object oriented mega widgets for tcl \\
jadetex & TeX macros used by Jade TeX output. \\
jed & A fast, compact editor based on the \\
jikes & Java source to bytecode compiler \\
jpilot-Mail & Mail plugin for jpilot \\
jpilot-syncmal & SyncMAL plugin for J-PILOT \\
kaffe & A free virtual machine for running Java(TM) \\
kaffe-devel & Development package with static libs and headers \\
kbiff & Kbiff is a new mail notification utility \\
kcpuload & Small applet which displays cpu time for \\
kdbg & A Graphical Debugger Interface \\
kdebase-devel & Devel stuff for kdebase \\
kdebase-nsplugins & Netscape Plugins for kdebase \\
kdegames-devel & KDE - Games - Headers and static \\
kdegames & KDE - Games \\
kdegraphics-devel & Header files for kdegraphics applications. \\
kde-i18n-ca & Catalan language support for KDE \\
kde-i18n-cs & Czech language support for KDE \\
kde-i18n-da & Danish language support for KDE \\
kde-i18n-el & Greek language support for KDE \\
kde-i18n-eo & Esperanto language support for KDE \\
kde-i18n-et & Estonian language support for KDE \\
kde-i18n-fi & Finnish language support for KDE \\
kde-i18n-he & Hebrew language support for KDE \\
kde-i18n-hu & Hungarian language support for KDE \\
kde-i18n-is & Icelandic language support for KDE \\
kde-i18n-ja & Japanese language support for KDE \\
kde-i18n-ko & Korean language support for KDE \\
kde-i18n-lt & Lithuanian language support for KDE \\
kde-i18n-nl & Dutch language support for KDE \\
kde-i18n-no & Norwegian language support for KDE \\
kde-i18n-no\_NY & Norwegian-Nynorsk language support for KDE \\
kde-i18n-pl & Polish language support for KDE \\
kde-i18n-pt\_BR & Brazil Portuguese language support for KDE \\
kde-i18n-pt & Portuguese language support for KDE \\
kde-i18n-ro & Romanian language support for KDE \\
kde-i18n-ru & Russian language support for KDE \\
kde-i18n-sk & Slovak language support for KDE \\
kde-i18n-sl & Slovenian language support for KDE \\
kde-i18n-sr & Serbian language support for KDE \\
kde-i18n-sv & Swedish language support for KDE \\
kde-i18n-tr & Turkish language support for KDE \\
kdemultimedia-devel & Header files for the kdemultimedia package \\
kdenetwork-devel & KDE- Network Applications Development \\
kdepim-devel & Devel stuff for kdepim \\
kdesdk-devel & Header files for kdesdk \\
kdetoys-devel & Headers and static libraries for kdetoys \\
kdev\_htdig & ht://Dig-Support for KDevelop \\
kernel22-secure & The Linux Kernel compiled for SMP machines. \\
kernel-doc & Various documentation bits found in the kernel \\
kernel-enterprise & The Linux Kernel compiled with options for \\
kernel-linus2.2 & The Linux kernel without patch (the real \\
kernel-linus2.4 & The Linux kernel without patch (the real \\
kernel-source & The source code for the Linux kernel. \\
klyx & KLyX - a word processor for the \\
knetload & Network traffic monitor \\
koffice-devel & Header files for developing koffice applications \\
kpl2 & Graphical presentation of data sets and functions \\
ktelnet & KTelnet is a frontend to the telnet \\
kudzu-devel & The development library for hardware probing. \\
kups-devel & Development files for usage of the kupsdconf \\
lame & Linux System Administration Made Easy \\
latex2html & LaTeX to HTML converter. \\
lbreakout & Breakout-style arcade game \\
leafnode & Leafnode - a leafsite NNTP server \\
lesstif-clients & Lesstif clients \\
lesstif-devel & Static library and header files for Lesstif/Motif-1.2 \\
lesstif-mwm & Lesstif Motif window manager clone based on \\
libblt2-devel & Headers of BLT \\
libblt2 & Libraries needed to use BLT \\
libclanlib0-devel & Headers for developing programs that will use \\
libclanlib0-gl & ClanLib OpenGL module \\
libclanlib0-magick & ClanLib ImageMagick module \\
libclanlib0 & Main library for clanlib \\
libclanlib0-mikmod & ClanLib MikMod module \\
libclanlib0-png & ClanLib PNG module \\
libc & The compatibility libraries needed by old libc.so.5 \\
libcurl1-devel & Header files and static libraries for libcurl \\
libdpsftp4-devel & Development package for libdpsftp \\
libdpsftp4 & Nice little FTP library not specific to \\
libelf & An ELF object file access library \\
libeMusic0 & Main library for eMusic \\
libetherx1 & A library for jabber. \\
libetherx1-devel & Package to make developpement with libetherx. \\
libffi & Foreign Function Interface \\
libfltk1-devel & Fast Light Too Kit (FLTK) - development \\
libfltk1 & Fast Light Tool Kit (FLTK) - main \\
libfnlib0 & Color font rendering library for X11R6. \\
libfnlib0-devel & Headers, static libraries and documentation for Fnlib. \\
libgcj-devel & Libraries for Java development using gcc \\
libgcj & Java runtime library for gcc \\
libgd1-devel & The development libraries and header files for \\
libgda0-devel & GNU Data Access Development \\
libglib2-devel & GIMP Toolkit and GIMP Drawing Kit support \\
libglib2 & Main library for glib \\
libglibwww1-devel & Development libraries, header files and utilities for \\
libglibwww1 & Libwww wrapper using glib event loop \\
libgnet0-devel & Header files for the Gnet library \\
libgnet0 & Libgnet, a network library \\
libgsl0-devel & Devel files for Scientific Library \\
libgsl0 & Shared librairies for Scientific Library \\
libgtkglarea5-devel & GtkGLArea is an OpenGL widget for GTK+ \\
libhermes1-devel & Headers for developing programs that will use \\
libhermes1 & Main library for hermes \\
libhylafax4-devel & Hylafax libraries \\
libhylafax4 & Hylafax libraries \\
libibtk0-devel & Libraries, includes and other files to develop \\
libibtk0 & Libraries, includes and other files to develop \\
libisdn4k-utils2-devel & Includes and other files to develop isdn4k-utils \\
libjbig-devel & Header files and static library for development \\
libmikmod2-devel & Header files and libraries for developing apps \\
libmorph0-devel & Headers and static libraries required for xmorph/gtkmorph \\
libnet & A C library for portable packet creation \\
libole20-devel & Libraries, includes, etc to develop libole2 applications \\
libpanelmm0-devel & Includes and other files to use panelmm \\
libpanelmm0 & Panel-- - A GTK-- wrapper for applet\_widget \\
libparted2-devel & Files required to compile software that uses \\
libparted2 & Files required to compile software that uses \\
libsafe & Stack Overflow protection \\
libsasl7-devel & Librairies for SASL a the Simple Authentication \\
libscrollkeeper0-devel & Includes and more to develop scrollkeeper applications \\
libSDL1.0 & Main library for SDL (old version) \\
libSDL\_image1.1-devel & Headers for developing programs that will use \\
libSDL\_image1.1 & Main library for SDL\_image \\
libSDL\_image1.1-test & Test binary for SDL\_image \\
libSDL\_net1.1-devel & Headers for developing programs that will use \\
libSDL\_net1.1 & Main library for SDL\_net \\
libSDL\_ttf1.2-devel & Headers for developing programs that will use \\
libSDL\_ttf1.2 & Main library for SDL\_ttf \\
libSDL\_ttf1.2-test & Test binary for SDL\_ttf \\
libskey2-devel & Libraries and headers for developing S/Key enabled \\
libskey2 & Libraries for S/Key enabled programs \\
libtclink & TrustCommerce C library \\
libtermcap2-devel & Development tools for programs which will access \\
libungif-progs & Programs for manipulating GIF format image files. \\
libunixODBC2-devel & Includes and static libraries for ODBC development \\
libusb0.1-devel & Libusb is a library which allows userspace \\
libusb0.1 & Libusb is a library which allows userspace \\
libwraster2-devel & Static libraries and header files \\
libwraster2 & Libraries needed by WindowMaker \\
libxml2-devel & Libraries, includes and other files to develop \\
libxml2 & The libXML library. \\
licq-autoreply & Autoreply Licq plugin \\
licq-console & Console based plugin for Licq that uses \\
licq-devel & Development files for Licq \\
licq-forwarder & Forwarder plugin for Licq \\
licq-rms & Remote management service plugin \\
licq-update-hosts & An auto update hosts plugin for Licq \\
lilo-doc & More doc for lilo \\
linuxconf-devel & The tools needed for developing linuxconf modules. \\
locales-am & Base files for localization (Amharic) \\
logcheck & Psionic LogCheck \\
lout-doc & The documentation for the Lout document formatting \\
lout & The Lout document formatting language. \\
lrzsz & The lrz and lsz modem communications programs. \\
ltrace & Tracks runtime library calls from dynamically linked \\
ltris & Nice tetris clone \\
lyx & A word processor for the Desktop Environment \\
macutils & Utilities for manipulating Macintosh file formats. \\
madbomber & Catch the bombs \\
Maelstrom & Maelstrom \\
mandrake\_doc-de & The Linux-Mandrake Installation Guide and User Guide, \\
mandrake\_doc-es & The Linux-Mandrake Installation Guide and User Guide, \\
mandrake\_doc-fr & The Linux-Mandrake Installation Guide and User Guide, \\
mandrake\_doc-it & The Linux-Mandrake Installation Guide and User Guide, \\
man-pages-cs & Czech Linux Manual Pages \\
man-pages-ja & japanese manual page \\
marbles & Atomix-style arcade game \\
mars-nwe & NetWare file and print servers which run \\
mathplot & Interactive function grapher \\
mcserv & Server for the Midnight Commander network file \\
mercury & The logic/functional programming language Mercury \\
Mesa-common-devel & Development files for GLU and glut libs \\
mgetty-contrib & User contributed stuff that comes with mgetty. \\
mm-devel & development files for mm. \\
mod\_sxnet & Strong Extranet module for mod\_ssl and apache \\
mon & A general-purpose resource monitoring system. \\
mozilla-devel & Mozilla development files \\
mozilla-irc & IRC support for Mozilla. \\
mozilla-mail & Mozilla-based mail system \\
mpeg2\_movie & Command line tools for generating MPEG2 movie \\
mpeg\_lib-devel & Mpeg library devel package \\
mxp & An X based Mandelbrot set generator and \\
MySQL-bench & MySQL - Benchmarks and test system \\
MySQL-client & MySQL - Client \\
MySQL-devel & MySQL - Development header files and libraries \\
MySQL & MySQL: a very fast and reliable SQL \\
MySQL-shared & MySQL - Shared libraries \\
nasm-doc & Extensive documentation for NASM \\
nasm-rdoff & Tools for the RDOFF binary format, sometimes \\
nasm & The Netwide Assembler, a portable x86 assembler \\
nautilus-devel & Libraries and include files for developing nautilus \\
nautilus-trilobite & Support for Eazel services \\
ncftp & An improved FTP client \\
nc & Reads and writes data across network connections \\
ncurses-extraterms & Some exotic terminal descriptions \\
nedit & A text editor for the X Window \\
netcdf-devel & Libraries to use the Unidata network Common \\
netscape-korean & Netscape in Korean \\
netscape-navigator & The Netscape Navigator Web browser \\
netscape-polish & Netscape in Polish \\
netscape-russian & Netscape in Russian \\
nil & NiL Isn't Liero \\
nmh & A capable mail handling system with a \\
nscd & A Name Service Caching Daemon (nscd) \\
nslint & a DNS lint checker \\
nss\_db-compat & NSS compatibility library for DB \\
nss\_db & NSS library for DB \\
ntp & Synchronizes system time using the Network Time \\
ocaml & The Objective Caml compiler and prog environment \\
ohphone & Initiate, or receive, a H.323 IP telephony \\
openh323\_1 & OpenH323 Library \\
openldap1 & LDAP servers and sample clients. \\
openuniverse & OpenGL Space Simulator \\
oregano & Oregano \\
p2c & A Pascal to C translator. \\
p2c-devel & Files for p2c Pascal to C translator \\
pam-doc & Additional documentation for pam \\
pan & A USENET newsreader for GNOME \\
pango-devel & System for layout and rendering of internationalized \\
parted & Flexible partitioning tool \\
pciutils-devel & Linux PCI development library \\
pdksh & A public domain clone of the Korn \\
penguin-command & A clone of the classic Missile Command \\
perl-Apache-Filter & Apache-Filter module for perl \\
perl-Apache-Session & Apache-Session module for perl \\
perl-Apache-SSI & Apache-SSI module for perl \\
perl-Array-RefElem & Array-RefElem module for perl \\
perl-Compress-Zlib & Compress-Zlib module for perl \\
perl-Convert-BER & Convert-BER (module for perl) \\
perl-Data-DumpXML & Data-DumpXML module for perl \\
perl-Date-Calc & Date-Calc module for perl (Data\_Type\_Utilities/Date) \\
perl-DateManip & DateManip module for perl \\
perl-DBIx-Recordset & DBIx-Recordset module for perl \\
perl-Devel-Symdump & Devel-Symdump module for perl \\
perl-ExtUtils\_F77 & Simple interface to F77 libs \\
perl-ExtUtils-PerlPP & ExtUtils-PerlPP module for perl \\
perl-File-NCopy & File-NCopy module for perl \\
perl-File-Tail & File-Tail mod for perl (File\_Names\_Sys\_Lock/File) \\
perlftlib & Libraries to use the FreeType library with \\
perl-GTK-GtkHTML & Perl module for the gtk+ GtkHTML library. \\
perl-HTML-Clean & HTML-Clean module for perl \\
perl-Image-Size & Image-Size module for perl \\
perl-libxml-enno & libxml-enno module for perl \\
perl-libxml-perl & libxml-perl module for perl \\
perl-Mail-Sendmail & Simple platform-independent mailer \\
perl-MLDBM & MLDBM module for perl \\
perl-Mon & perl-Mon module \\
perl-MP3-Info & Perl module to manipulate / fetch info \\
perl-Mysql & DBD Mysql perl Emulation Layer \\
perl-Net-IPv4Addr & Perl modules to manipulates Ipv4 addresses \\
perl-Net-Telnet & Net::Telnet (module for perl) Jay Rogers <jay@rgrs.com> \\
perl-Net-XWhois & xtensible client framework for doing Whois queries \\
perl-Parse-RecDescent & Parse-RecDescent mod for perl \\
perl-Parse-Yapp & Parse-Yapp module for perl \\
perl-PDA-Pilot & Perl module for Palm \\
perl-PDL-doc & PerlDL documentation package \\
perl-Period & Time::Period module for perl \\
perl-SDL & Wrapper around the cross platform Simple DirectMedia \\
perl-SGMLSpm & Perl library for parsing the output of \\
perl-Storable & Storable module for perl \\
perl-Tie-Cache & Tie-Cache module for perl \\
perl-TimeDate & TimeDate module for perl (Data\_Type\_Utilities/Time) \\
perl-Time-HiRes & Time-HiRes module for perl (Data\_Type\_Utilities/Time) \\
perl-Tk-devel & Tk modules for Perl (development package) \\
perl-Tk-doc & Tk modules for Perl (documentation package) \\
perl-XML-Parser & XML-Parser module for perl \\
perl-XML-RSS & XML-RSS module for perl \\
perl-XML-XSLT & XML-XSLT module for perl \\
php-dba\_gdbm\_db3 & A dba-gdbm-db3 module for PHP4 \\
php-devel & Development package for PHP4 \\
php-gd & GD module for PHP4 \\
phpgroupware & phpGroupWare is a web-based groupware suite written \\
php-imap & IMAP module for PHP4 \\
php-ldap & IMAP module for PHP4 \\
php-manual\_en & English version of the PHP Manual \\
php-mysql & MySQL module for PHP4 \\
php-pgsql & PostgreSQL module for PHP4 \\
php-readline & Readline module for PHP4 \\
php-tclink & TrustCommerce payment module for PHP4 \\
pilot-link-devel & PalmPilot development header files \\
pilot-link-tcl & Tcl module for Palm \\
pine & A commonly used, MIME compliant mail and \\
pingus & Pingus - A free Lemmings clone \\
plugger & A generic netscape plug-in \\
portsentry & Psionic PortSentry \\
postgresql-devel & PostgreSQL development header files and libraries. \\
postgresql-jdbc & Files needed for Java programs to access \\
postgresql-tcl & A Tcl client library, and the PL/Tcl \\
postgresql-test & The test suite distributed with PostgreSQL. \\
postgresql-tk & Tk shell and tk-based GUI for PostgreSQL. \\
powermanga & Shoot them up with 3d graphics \\
publib-devel & C function library \\
pump-devel & Header files and static libs for the \\
pwdb-devel & pwdb include file and link library \\
pwlib1-devel & Portable Windows Libary development files \\
pwlib1 & Portable Windows Libary \\
pyDict & pyDict - A English/Chinese Dictionary written with \\
pygnome-applet & Python bindings for GNOME Panel applets \\
pygnome-capplet & Python bindings for GNOME Panel applets \\
pygnome-libglade & GNOME support for the libglade python wrapper \\
pygnome & The sources for the PyGTK and PyGNOME \\
pygtk-glarea & A wrapper for the GtkGLArea widget for \\
pygtk-libglade & A wrapper for the libglade library for \\
pysol & PySol provides several solitaire card games \\
python-docs & Documentation for the Python programming language \\
python-imaging & Python's own image processing library \\
python-numeric-devel & Python numerical facilities \\
qcad & A professional CAD system \\
qt2-static-libraries & Version of the Qt GUI toolkit for \\
qtrans & Natural language translation utility \\
quanta & A web editor for the KDE Desktop \\
radvd & The IPv6 Router Advertisement Daemon \\
R-base & A language for data analysis and graphics \\
recode-devel & GNU recode devel \\
rep-gtk-libglade & Librep binding for the libglade library for \\
rio500-devel & Header files and static libraries needed for \\
rocksndiamonds & A boulderdash like \\
rpm-rebuilder & Tools to build/check distributions \\
rrdtool-devel & RRDtool - round robin database static libraries \\
ruby-devel & Development file for the powerful language Ruby \\
ruby-doc & Documentation for the powerful language Ruby \\
ruby-gtk & Ruby extension library to use Gtk+. \\
ruby & Object Oriented Script Language \\
ruby-tk & Tk extension for the powerful language Ruby \\
rute & Rute Users Tutorial and Exposition \\
sawfish-themer & A GUI for creating sawfish window manager \\
screem & Web Site CReating and Editing EnvironMent \\
sendmail-cf & The files needed to reconfigure Sendmail \\
sendmail-doc & Documentation about the Sendmail Mail Transport Agent \\
sfm & A Simple File Manager \\
sketch & Drawing tool \\
skey & S/Key suite of programs \\
slang-doc & Extra documentation for slang libraries \\
slap & SLAP - SEIKO SmartLabel Printing Utility \\
slrn-pull & Offline news reading support for slrn \\
SmallEiffel & The GNU Eiffel Compiler and Libraries \\
smalltalk & Smalltalk free language implementation \\
smpeg-player & Simple MPEG player baed on smpeg library \\
sndconfig & The Red Hat Linux sound configuration tool. \\
sox-devel & The SoX sound file format converter libraries. \\
spacecup & 3d ice-hockey or football in the space \\
spellutils & Programs for helping spell checking. \\
spruce & The Spruce Mail Client \\
statserial & A tool which displays the status of \\
stunnel & Program that wraps normal socket connections with \\
surfraw & Shell Users' Revolutionary Front Rage Against the \\
svgalib & A low-level fullscreen SVGA graphics library \\
svgalib-devel & Development tools for programs using the SVGAlib \\
SVGATextMode & A utility for improving the appearance of \\
swatch & A utility for monitoring system logs files. \\
swig-devel & Header files and libraries for developing apps \\
swig & Simplified Wrapper and Interface Generator (SWIG) \\
swi-prolog & Prolog interpreter and compiler. \\
t1lib1-devel & Type 1 font rasterizer \\
taipeifonts & taipei chinese big5 fonts \\
talk-server & Server for the talk program \\
tcllib & Library of utility modules for tcl. \\
tclx & Tcl/Tk extensions for POSIX systems. \\
tcp\_wrappers-devel & A security library which acts as a \\
tetex-afm & A converter for PostScript(TM) font metric files, \\
tetex-doc & The documentation files for the TeX text \\
tetex-dvilj & A DVI to HP PCL (Printer Control \\
tetex-dvipdfm & A DVI to PDF converter \\
tetex-dvips & A DVI to PostScript converter for the \\
tetex-latex & The LaTeX front end for the TeX \\
tetex & The TeX text formatting system \\
tetex-xdvi & An X viewer for DVI files \\
teyjus & Lambda Prolog - a higher-order logic programming \\
tftp-server & The server for the Trivial File Transfer \\
timidity-instruments & Instruments for the timidity midi->wave converter/player \\
TiMidity++ & MIDI to WAVE converter and player \\
tix & A set of capable widgets for Tk. \\
tkcvs & Tk interface for CVS \\
tkinter & A graphical user interface for the Python \\
tk & Tk GUI toolkit for Tcl, with shared \\
tripwire & A system integrity assessment tool. \\
ttfprint & ttfprint generates Chinese compliant postscript files for \\
tuxkart & Tuxedo T. Penguin stars in Tuxkart \\
ucd-snmp-devel & The development environment for the UCD-SNMP project. \\
units & A utility for converting amounts from one \\
unixODBC-gui-gtk & ODBC configurator based on GTK+ and GTK+ \\
unixODBC-gui-qt & ODBC configurator, Data Source browser and ODBC \\
utf-converter & Various UTF-7/8 <-> bg5,gb... converter \\
vdk & A C++ framework that wraps famous Gtk+ \\
VFlib2-devel & header files and static library for VFlib \\
VFlib2 & The vector font library (VFlib2) \\
vimguide & Vim editor reference guide \\
vnc-doc & Documentation about VNC \\
vnc-java & Java interface to VNC \\
vnc-server & Virtual Network Computing - Server \\
vnc-SVGALIB & Virtual Network Computing - SVGALIB client \\
vnc & Virtual Network Computing - Client \\
w3c-libwww-apps & Applications built using Libwww web library: e.g. \\
w3c-libwww-devel & Libraries and header files for programs that \\
w3c-libwww & HTTP library of common code \\
WindowMaker & A window manager for the X Window \\
WindowMaker-devel & Static libraries and header files \\
wine-devel & MS-Windows emulator - Devel files \\
wine & MS-Windows emulator \\
wireless-tools & Wireless ethernet configuration tools \\
wmnet & Applet that monitors the network \\
WMRack & A WindowMaker Dock CD+Sound Applet \\
WsLib-devel & Widgetset for the Linux FrameBuffer device \\
wu-ftpd & An FTP daemon originally developed by Washington \\
wv-devel & MSWord 6/7/8/9 binary file format -> HTML \\
X11R6-contrib & A collection of user-contributed X Window System \\
x3270 & An X Window System based IBM 3278/3279 \\
xaos-aalib & Real-time fractal zoomer, aalib package \\
xaos & A real-time fractal zoomer \\
xaos-svgalib & Real-time fractal zoomer, svgalib package \\
xawtv-misc & Xawtv miscellous stuff \\
xawtv-radio & Xawtv radio support \\
xboard & An X Window System graphical chessboard \\
xdelta-devel & Static libraries and header files for development \\
xdosemu & A DOS emulator for the X Window \\
xearth & An X display of the Earth from \\
xemacs & An X Window System based version of \\
xemacs-extras & Files that XEmacs has in common with \\
xemacs-info & Information files for XEmacs. \\
xemacs-mule & The XEmacs binary with mule (MUlti-Lingual Emacs) \\
xemacs-pcomplete & Programmable completion for XEmacs \\
xemacs-tramp & Transparent Remote (file) Access, Multiple Protocol \\
xerces-c-devel & XML parser for developer \\
xerces-c-manual & Online manual for Xerces-C \\
xfce & Lightweight desktop environment \\
xfishtank & An X Window System graphic display of \\
XFree86-doc & Documentation on various X11 programming interfaces \\
XFree86-static-libs & X11R6 static libraries \\
XFree86-Xvfb & A virtual framebuffer X Windows System server \\
xinetd-ipv6 & Xinetd is a powerful replacement for inetd. \\
xinput & Runtime configuration and test of XInput devices \\
xlispstat & An implementation of the Lisp language with \\
xml-i18n-tools & This module contains some utility scripts and \\
xmms-diskwriter & DiskWriter output backend \\
xmms-kjofol-skins & XMMS - Vis plugin to get kjofol \\
xmms-mesa & Visualization plugins that use the Mesa3d library \\
xmms-more-vis-plugins-unsafe & XMMS - More visualization plugins (unsafe ones, \\
xmms-more-vis-plugins & XMMS - More visualization plugins. \\
xoscope & A digital oscilloscope program for your sound \\
xosview & An X Window System utility for monitoring \\
xpaint & An X Window System image editing or \\
xpat2 & A set of Solitaire type games for \\
xpcd-gimp & GIMP 0.99 plugin, makes xpcd and gimp \\
xpcd & PhotoCD tool collection \\
xpcd-svga & SVGAlib viewer for PhotoCD images \\
xpilot & An X Window System based multiplayer aerial \\
xrally & A clone of the Rally X arcade \\
xsane & Xsane is a frontend for the scanner \\
xscavenger & Cool arcade/thinking game very much like Lode \\
xscreensaver-gl & A set of GL screensavers \\
xsoldier & Shooting game on X Window System \\
xsysinfo & An X Window System kernel parameter monitoring \\
xtoolwait & A utility which aims to decrease X \\
xtraceroute & Graphical OpenGL version of traceroute \\
xwc & A filemanager for X \\
xwpe & An X Window System programming environment \\
xwpe-X11 & The X programs needed for the Xwpe \\
xxgdb & An X Window System graphical interface for \\
yodl & Yet oneOther Document Language. \\
yudit & Unicode Text Editor \\
zgv & A viewer for many different image formats. \\
zsh-doc & The doc package of zsh \\
\hline
\end{supertabular}\label{lbl_paquetes_redhat} 
} 
\end{center} 
