% Linux Installation and Getting Started    -*- TeX -*-
% chap-xwindows.tex.
% Copyright (c) 1992, 1993 by Matt Welsh <mdw@sunsite.unc.edu>
%
% This file is freely redistributable, but you must preserve this copyright 
% notice on all copies, and it must be distributed only as part of "Linux 
% Installation and Getting Started". This file's use is covered by the 
% copyright for the entire document, in the file "copyright.tex".
%
% Copyright (c) 1998 by Specialized Systems Consultants Inc. 
% <ligs@ssc.com>
%Revision 5 de julio 2002 por Francisco Javier Fernández <serrador@arrakis.es>
%Gold

%\chapter{The X Window System}\label{chap-xwindows}
\chapter{El Sistema X-Window}
\label{chap-xwindow}
\markboth{El Sistema X-Window}{}

% derived from the monstrous "advanced features" chapter.
\index{X~Window~System|(}
\index{X~Window~System!definición}
\markboth{Características Avanzadas}{El Sistema X~Window}

%The X~Window System is a graphical user interface (GUI) that was
%originally developed at the Massachusetts Institute of
%Technology. Commercial vendors have since made X the industry standard
%GUI for UNIX platforms. Virtually every UNIX workstation in the world
%now runs some form of X.

El sistema X-Window es una interfaz gráfica para usuario (``GUI''
en sus siglas en inglés), que se desarrolló originalmente en el Instituto de Tecnología de Massachussetts (Massachusetts Institute of
 Technology, más conocido como MIT). X es la ``GUI'' estándar para plataformas UNIX
 comerciales. Prácticamente todas las estaciones de trabajo UNIX del
 mundo trabajan bajo alguna forma de X.


\index{X11R6}
\index{XFree86}
%A free port of the MIT X~Window System version 11, release 6 (X11R6)
%for 80386, 80486, and Pentium UNIX systems was developed by a team of
%programmers that was originally headed by David Wexelblat. This
%release, known as XFree86\footnote{XFree86 is a trademark of The
%XFree86 Project, Inc.}, is available for System V/386, 386BSD, and
%other Intel x86 UNIX implementations, including Linux. It provides all
%of the binaries, support files, libraries, and tools required for
%installation.

Un equipo  de programadores encabezados inicialmente por David Welxelblat 
desarrollaron un porte libre del sistema X-Window del MIT,
versión 11 y ``release'' 6 (X11R6) para sistemas UNIX con 80386, 80486
y Pentium. Esta ``release'', conocida como
XFree86\footnote{XFree86 es una marca registrada por XFree86 Project,
  Inc.}, está disponible para sistemas V/386, 386BSD y otras
implementaciones UNIX de Intel x86, incluyendo {\linux}. Proporciona
todos los binarios, ficheros de soporte, bibliotecas y utilidades para
la instalación. 

%Some features offered by this release are:
%\begin{itemize}
%\item complete inclusion of the X Consortium's X11R6.3 release;
%\item a new DPMS extension, donated by Digital Equipment Corporation;
%\item the Low Bandwidth X (LBX) extension in all X servers;
%\item Microsoft IntelliMouse support;
%\item support for {\tt gzip} font compression.
%\end{itemize}

Algunas de las características que ofrece esta versión son:
\begin{itemize}
\item Inclusión de la versión completa de X11R6.3 del {\em X Consortium}.
\item Una nueva extensión ``DPMS'', donada por Digital Equipment
  Corporation.
\item La extensión de {\em Low Bandwidth X}(LBX) en todos los
  servidores X.
\item Soporte {\em Microsoft Intellimouse}
\item Soporte para la compresión de fuentes {\tt gzip}
\end{itemize}

%To use the X Window System, you are encouraged to read {\em The
%X~Window System: A User's Guide\/} (see Appendix~\ref{app-info}).
%Here, we describe step-by-step an XFree86 installation under Linux.
%You still need to fill in some of the details by reading the XFree86
%documentation, which is discussed below.  The Linux {\em XFree86 HOW
%TO\/} is another good information source.

Para usar el sistema X-Window, se recomienda leer {\em The X-Window
  System: A User's Guide\/} (ver Apéndice). Aquí
  describiremos paso a paso la instalación de XFree86 bajo {\linux}. Debe
  fijarse en algunos detalles leyendo la documentación de XFree86, que
  se discute más adelante. El {\em XFree86 CÓMO\/} de {\linux} es otra fuente de
  información interesante.
%%% Input each section

\input{advanced/xwindows}







